DOM bridges and barriers: systematic review and survey

### 2025-09-27 reports/draft_results.qmd
stack bar and radar plots

@@

>>>>

theme_ms <- function(){
  theme_minimal() %+replace%    
    theme(axis.text = element_text(size = 14, color = "black"), 
          axis.title = element_text(size = 16, color = "black"), 
          strip.text = element_text(size = 13, color = "black"))
}

@@

#format data
freq_job_survey <- code_vars_s %>% 
  select(c(1, 21:54)) %>% 
  janitor::clean_names() %>%
  pivot_longer(2:35, names_to = "sub_theme", values_to = "total") %>%
  group_by(survey, sub_theme) %>%
  summarise(total = sum(total), 
            .groups = "drop") %>%
  mutate(fish_ship = ifelse(str_detect(survey, "WhaleWatch"), "Shipping", "Fishing"))

lib_job_survey <- code_freq_s %>%
  mutate(id = paste(bridge_barr, code_cat, code_name, sep = "_")) %>% 
  select(id)

freq_job_survey$id <- NA
for(i in 1:nrow(freq_job_survey)){
  curr_code = freq_job_survey$sub_theme[i]
  curr_id = lib_job_survey$id[agrepl(curr_code, lib_job_survey$id, 6)]

  freq_job_survey$id[i] <- curr_id

}

freq_job_survey$id[freq_job_survey$sub_theme == "stigmatization"] <- "Barrier_Social barrier_Stigmatization"
freq_job_survey$id[freq_job_survey$sub_theme == "cost"] <- "Barrier_Social barrier_Cost"

freq_job_survey <- freq_job_survey %>%
  separate_wider_delim(id, delim = "_", names = c("bridge_barr", "code_cat", "code_name"))

freq_job_survey$bridge_barr <- factor(freq_job_survey$bridge_barr, levels = c("Bridge", "Barrier"))

#calculate proportions
freq_job_survey2 <- freq_job_survey %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_cat) %>% 
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(code_level = if_else(code_cat %in% c("Ecological barrier", "Ecological bridge"), "Ecological bridge or barrier", 
                              if_else(code_cat %in% c("Data barrier", "Data bridge"), "Data bridge or barrier",
                              if_else(code_cat %in% c("Social barrier", "Social bridge"), "Social bridge or barrier", 
                              if_else(code_cat %in% c("Implementation bridge", "Implementation barrier"), "Implementation bridge or barrier", NA)))), 
          id = paste(fish_ship, bridge_barr, code_cat)) %>%
  distinct(id, .keep_all = TRUE)

#stacked bar plots
stack_survey <- ggplot(freq_job_survey2, aes(fill=code_level, y=value, x=fish_ship)) + 
    geom_bar(position="stack", stat="identity") +
    scale_fill_manual(values = c("#CFE2F3", "#C5E0B4","royalblue4","#45818E")) +
    facet_wrap(~bridge_barr) +
    labs(fill = "Sub-theme") +
    theme_ms() +
    xlab("") + 
    ylab("Proportion of theme (%)")

#radar plots
freq_job_survey3 <- freq_job_survey %>%
  group_by(fish_ship, bridge_barr) %>%
  mutate(n_total = sum(total)) %>%
  ungroup() %>%
  group_by(fish_ship, bridge_barr, code_name) %>% 
  mutate(n_subtotal = sum(total)) %>%
  reframe(value = (n_subtotal/n_total)*100) %>%
  ungroup() %>%
  mutate(id = paste(fish_ship, bridge_barr, code_name)) %>%
  distinct(id, .keep_all = TRUE) %>%
  select(-c(id))

top_survey <- freq_job_survey3 %>% group_by(fish_ship, bridge_barr) %>% arrange(desc(value)) %>% top_n(3) %>% ungroup()

top_bridge <- top_survey %>% 
  filter(bridge_barr == "Bridge") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

top_barrier <- top_survey %>% 
  filter(bridge_barr == "Barrier") %>% 
  pivot_wider(names_from = code_name, values_from = value) %>% 
  select(-bridge_barr) %>%
  mutate_all(~replace_na(., 0))

radar_br_survey <- ggradar::ggradar(top_bridge,
        values.radar = c(0, 14, 22), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "bottom", 
        fill = TRUE, 
        axis.label.size = 3.5)

radar_ba_survey <- ggradar::ggradar(top_barrier,
        values.radar = c(0, 17, 28), 
        background.circle.colour = "white",
        axis.line.colour = "gray60",
        gridline.min.colour = "gray60",
        gridline.mid.colour = "gray60",
        gridline.max.colour = "gray60",
        group.colours = c("#F29325", "#007172"),
        legend.position = "none", 
        fill = TRUE, 
        axis.label.size = 3.5)

stack_survey | radar_br_survey | radar_ba_survey
```
